Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-09-18 Manuscript.Rmd
update to manuscript

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey & Joseph T. McGuire"
output:
  word_document: 
    reference_docx: Style_reference.docx
  pdf_document: default
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

``` {r Libraries and functions, include = FALSE, fig.align="center", fig.width=6, fig.height=4, echo=FALSE}

@@

## tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
# This takes either a matrix of correlation values (vectors too, but manually compute pvals)
# Normalization approach suggested in network textbook (equation 7.10)
fisherTanh <- function(Data = padjMatrix){

@@

@@

@@

``` {r ROI computation, echo=FALSE, message = FALSE}
  ## ROI definition
  # First, load the raw count csv files
  valCounts <- read.csv2('decCounts.csv', sep = ",")
  dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")

@@

```{r Meta-analysis ROIs, out.width="60%", fig.align = "center", fig.cap= "Figure 1. Template atlas from Glasser et al. (2016) (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom). Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
include_graphics("./Images/ROIS2.png")
```

@@

```{r Template partition, out.width="60%", fig.align = "center", fig.cap = "Figure 2. Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}

@@

``` {r Partition comparison: all cross-method agreement, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE, fig.cap = "Figure 3. Distribution of ARI indices when comparing modularity and spectral partitioning. The distribution shows overall high agreement. (Will probably remove this figure)"}
# Cross-method
# Don't worry about plotting, since that's mainly for a general visualization
RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary","Membership"), nSubjects = length(Summaries), subjNames = subjList)

@@

``` {r Partition comparison: all 2 plot, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 4. Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}

# par(mfrow = c(1,2))
# corrplot(RI_all_between,
#          is.corr = F, 
#          method = "color", 
#          tl.pos = "n", 
#          tl.col = "black", 
#          cl.lim = c(0,1),
#          cl.pos = "b",
#          cl.length = 3)
# mtext("Subjects", side = 2, line = -4.5, cex = 1.5)
# mtext("Subjects", side = 3, line = 4.5, cex = 1.5)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "b")
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black",
         cl.pos = "n", 
         add = T)

@@

``` {r Partition comparison: halves plot, fig.align="center", fig.width = 6, fig.height = 4, fig.cap = "Figure 5. Similarity matrices showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right). These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
# plots
par(mfrow=c(1,2))
corrplot(RI_all_between_halves, 
         is.corr = F, 
         method = "color",
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.8,
         cl.pos = "b",
         cl.length = 3)
corrplot(RI_PCC_halves, 
         is.corr = F,     
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.col = "black", 
         tl.cex = 0.8,
         cl.lim = c(-0.03,1),
         cl.length = 3)
corrplot(RI_PFC_halves, 
         is.corr = F, 
         method = "color",
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.8,
         cl.pos = "n", 
         add = T)

@@

``` {r Partition comparison: halves ratios, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 6. mPFC displays higher within-subject agreement than between subjeccts, as evidenced by a high within/between subject mean ARI. PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE, cache = TRUE}
# Now compare all possible pairs of subjects
# Compare all halves with RI
RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)

@@

``` {r Partition comparison: session similarity matrices plot, fig.align="center", fig.width = 6, fig.height = 4, fig.cap = "Figure 7. Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right). The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.pos = "b",
         cl.length = 3)
corrplot(RI_PCC_sess, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.length = 3)
corrplot(RI_PFC_sess, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         add = T)

# Now run comparisons among all subjects
RI_all_between_sess <- comparePartitions(Data = Summaries_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
tempComm_PCC_sess <- lapply(Summaries_sess, "[", i = posteriorIndx, j =)
tempComm_PFC_sess <- lapply(Summaries_sess, "[", i = !posteriorIndx, j =)
RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)

@@

``` {r Partition comparison: session ratios, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 8. Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions. Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE, cache = TRUE}
## Brain storming:
## Within-subject comparisons would be more interesting? Like, comparing the mean RI within-between per subject
## Perhaps a more interresting idea would be to generate an index of variance within/between subject
## These are just attempts at that are not perfect:

@@

``` {r Stability per subject: Overall, fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 9. ARI between communities computed at each sliding epoch and the original partition for all subjects (left), as well as the distribution of ARI standard deviations per subject (right).", echo=FALSE, message = FALSE, cache = TRUE}
# Load files
setwd('./Sliding_window/')
temp <- list.files(pattern = '*Comparisons.csv')
SC <- lapply(temp, read.csv2)
temp <- list.files(pattern = '*Values.csv')
SVals <- lapply(temp, read.csv2)

@@

``` {r Stability per subject: Fiedler vector vs prop. DMN plot, fig.align="center", fig.width=3.5, fig.height=3.5, fig.cap = "Figure 10. Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows. Grey lines denote each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
# Fiedler Vector x proportion of times a vertex was affiliated with DMN
SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
  #geom_point(aes(FiedlerVec, slidePropDMN, fill = SubjID), show.legend = F, alpha = 0.05, pch = 21, color = "black") + 
  geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
  theme_classic()

@@

``` {r Noise Effects: tSNR Comparison, fig.align="center", fig.width=3.5, fig.height=3.5, fig.cap = "Figure 12. Mean tSNR for mPFC and PCC across participants. This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE, cache = TRUE}
## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
# Flexibility vs SNR
# Are vertices with lower SNR switching communities more often?
SNR_vs_Flex <- sapply(Summaries, function(data) cor(data$varCoeff, data$slideFlexibility))

@@

``` {r Noise Effects: Per-subject Fiedler by R-sqd, fig.align="center", fig.width=4, fig.height=4, fig.cap = "Figure 13. Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DMN time series.", echo=FALSE, message = FALSE, cache = TRUE}
setwd('./Variance/')
temp <- list.files()
Variance <- lapply(temp, read.csv)

@@

``` {r Noise Effects: R-sqd vs tSNR, fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 15. Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the least tSNR (left). However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE, cache = TRUE}
# grid.arrange(v6, v7, ncol = 2)
# par(mfrow = c(1,2))
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "R-squared Value",
#               ylab = "Z-Coordinate")
# 
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$varCoeff, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "Coefficient of Variation (SNR)",
#               ylab = "")

@@

``` {r Correlation vs community detection: comparison plot, fig.align="center", fig.width=4, fig.height=4, fig.cap = "Figure 17. Day 1 vs Day 2 oefficients of spatial correlations for every method, as well as between methods. Community detection through spectral partitioning provides the most stable inter-day estimates, even though both methods show good level of agreement.", echo=FALSE, message = FALSE}
# Day 1 vs Day 2 Spatial Correlation Comparison
prepostComp_plot <- ggplot(data = prepostComp, aes(Approach, Correlation, fill = Approach)) +
  geom_boxplot(show.legend = F) +
  labs(x = "", y = "Correlation Coefficient") +
  ylim(0,1) +
  theme(text = element_text(size=35)) +
  theme_classic()
prepostComp_plot
```

@@

## Acknowledgements
Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.

>>>>

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey^1^ & Joseph T. McGuire^1^"
output:
  pdf_document: default
  html_document: default
  word_document: 
    reference_docx: Style_reference.docx
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

```{r Libraries and functions, include = FALSE, fig.align="center", fig.width=6, fig.height=4, echo=FALSE}

@@

## tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
# This takes either a matrix of correlation values (vectors too, but manually compute pvals)
# Normalization approach suggested in network textbook (equation 7.10)
fisherTanh <- function(Data = padjMatrix){

@@

1. Department of Psychological and Brain Sciences, Boston University, Boston, USA

Corresponding author:

\newpage

@@

**Keywords:** brain networks; DMN; individual differences

\newpage

@@

``` {r ROI computation, echo=FALSE, message = FALSE}

  ## ROI definition
  # First, load the raw count csv files
  valCounts <- read.csv2('decCounts.csv', sep = ",")
  dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")

@@

```{r Meta-analysis ROIs, out.width = "60%", fig.align = "center", fig.cap= "Figure 1. Template atlas from Glasser et al. (2016) (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom). Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}

include_graphics("./Images/ROIS2.png")

@@

```{r Template partition (Fig. 2), out.width="60%", fig.align = "center", fig.cap = "Figure 2. Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}

@@

``` {r Partition comparison: all cross-method agreement (Fig. 3), fig.align="center", fig.width=3.5, fig.height=3.5, echo=FALSE, message = FALSE, cache = TRUE, fig.cap = "Figure 3. Distribution of ARI indices when comparing modularity and spectral partitioning. The distribution shows overall high agreement. (Will probably remove this figure)"}
# Cross-method
# Don't worry about plotting, since that's mainly for a general visualization
RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary","Membership"), nSubjects = length(Summaries), subjNames = subjList)

@@

``` {r Partition comparison: all 2 plot, fig.align="center", out.width = "40%", fig.cap = "Figure 4. Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}

# par(mfrow = c(1,2))
# corrplot(RI_all_between,
#          is.corr = F, 
#          method = "color", 
#          tl.pos = "n", 
#          tl.col = "black", 
#          cl.lim = c(0,1),
#          cl.pos = "b",
#          cl.length = 3)
# mtext("Subjects", side = 2, line = -4.5, cex = 1.5)
# mtext("Subjects", side = 3, line = 4.5, cex = 1.5)
par(xpd=T)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.1, 
         cl.lim = c(0,1),
         cl.length = 3,
         addgrid.col = "grey99",
         cl.pos = "r",
         mar = c(1,0,2,0))
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.cex = 0.1,
         cl.pos = "n",
         addgrid.col = "grey90",
         mar = c(1,0,2,0), 
         add = T)
mtext(expression(bold("Subject Partitions")), line = 0.8)
mtext(expression(bold("Subject Partitions")), side = 2, line = -2.5)
mtext(expression(bold("PFC")), line = 0, at = par("usr")[1]+0.7*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.22*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Partition comparison: halves plot, fig.align="center", out.width = "60%", fig.cap = "Figure 5. Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right). These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
# plots
par(mfrow=c(1,2))
corrplot(RI_all_between_halves, 
         is.corr = F, 
         method = "color",
         addgrid.col = "grey90",
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.1,
         cl.pos = "n",
         cl.lim = c(0,1),
         cl.length = 3,
         mar = c(1,1,1,1))
mtext("Subjects (Day 1 and Day 2)", line = 0)
mtext("Subjects (Day 1 and Day 2)", side = 2, line = 3)
corrplot(RI_PCC_halves, 
         is.corr = F,     
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.col = "black", 
         tl.cex = 0.1,
         cl.lim = c(0,1),
         cl.pos = "r",
         addgrid.col = "grey90",
         cl.length = 3)
mtext("Subjects (Day 1 and Day 2)", line = 0)
corrplot(RI_PFC_halves, 
         is.corr = F, 
         method = "color",
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.1,
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)

@@

``` {r Partition comparison: halves ratios (Fig. 6), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 6. mPFC displays higher within-subject agreement than between subjeccts, as evidenced by a high within/between subject mean ARI. PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE, cache = TRUE}
# Now compare all possible pairs of subjects
# Compare all halves with RI
RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)

@@

``` {r Partition comparison: session similarity matrices plot, fig.align="center", out.width = "60%", fig.cap = "Figure 7. Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects). The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.pos = "b",
         cl.length = 3)
corrplot(RI_PCC_sess, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.length = 3)
corrplot(RI_PFC_sess, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         add = T)
```

``` {r Partition comparison: session compare all, echo=FALSE, message = FALSE, cache = TRUE}
# Now run comparisons among all subjects
RI_all_between_sess <- comparePartitions(Data = Summaries_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
tempComm_PCC_sess <- lapply(Summaries_sess, "[", i = posteriorIndx, j =)
tempComm_PFC_sess <- lapply(Summaries_sess, "[", i = !posteriorIndx, j =)
RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)

@@

``` {r Partition comparison: session ratios (Fig. 8), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 8. Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions. Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE, cache = TRUE}
## Brain storming:
## Within-subject comparisons would be more interesting? Like, comparing the mean RI within-between per subject
## Perhaps a more interresting idea would be to generate an index of variance within/between subject
## These are just attempts at that are not perfect:

@@

``` {r Stability per subject: Overall (Fig. 9), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 9. ARI between communities computed at each sliding epoch and the original partition for all subjects (left), as well as the distribution of ARI standard deviations per subject (right).", echo=FALSE, message = FALSE, cache = TRUE}
# Load files
setwd('./Sliding_window/')
temp <- list.files(pattern = '*Comparisons.csv')
SC <- lapply(temp, read.csv2)
temp <- list.files(pattern = '*Values.csv')
SVals <- lapply(temp, read.csv2)

@@

``` {r Stability per subject: Fiedler vector vs prop. DMN plot, fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 10. Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows. Grey lines denote each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
# Fiedler Vector x proportion of times a vertex was affiliated with DMN
SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
  #geom_point(aes(FiedlerVec, slidePropDMN, fill = SubjID), show.legend = F, alpha = 0.05, pch = 21, color = "black") + 
  geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
  theme_classic()

@@

``` {r Noise Effects: tSNR Comparison (Fig. 12), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 12. Mean tSNR for mPFC and PCC across participants. This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE, cache = TRUE}
## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
# Flexibility vs SNR
# Are vertices with lower SNR switching communities more often?
SNR_vs_Flex <- sapply(Summaries, function(data) cor(data$varCoeff, data$slideFlexibility))

@@

``` {r Noise Effects: Per-subject Fiedler by R-sqd (Fig. 13), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 13. Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DMN time series.", echo=FALSE, message = FALSE, cache = TRUE}
setwd('./Variance/')
temp <- list.files()
Variance <- lapply(temp, read.csv)

@@

``` {r Noise Effects: R-sqd vs tSNR (Fig. 15), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 15. Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the least tSNR (left). However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE, cache = TRUE}
# grid.arrange(v6, v7, ncol = 2)
# par(mfrow = c(1,2))
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "R-squared Value",
#               ylab = "Z-Coordinate")
# 
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$varCoeff, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "Coefficient of Variation (SNR)",
#               ylab = "")

@@

``` {r Correlation vs community detection: comparison plot (Fig. 17), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 17. Day 1 vs Day 2 oefficients of spatial correlations for every method, as well as between methods. Community detection through spectral partitioning provides the most stable inter-day estimates, even though both methods show good level of agreement.", echo=FALSE, message = FALSE}
# Day 1 vs Day 2 Spatial Correlation Comparison
prepostComp_plot <- ggplot(data = prepostComp, aes(Approach, Correlation, fill = Approach)) +
  geom_boxplot(show.legend = F) +
  labs(x = "", y = "Correlation Coefficient") +
  ylim(0,1) +
  theme(text = element_text(size=35)) +
  theme_classic()
prepostComp_plot
```

@@

## Acknowledgements

Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
